Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/experiments.tex

In all experimental settings, we use the learning algorithm described in
alg.~\ref{alg:dau} and \TODO{supplementary, algo 1}. The variant of DDPG and DQN
used are described in the supplementary material, as well as all the hyperparameters
used. To make comparison fair, we still use rescaled discount factor $\gamma_\deltat$ and reward $r_\deltat$  as defined in equations \TODO{ref}, as well as scaled learning rates for DDPG and DQN.

>>>>

In all settings, we use the learning algorithm described in
Alg.~\ref{alg:dau} and \TODO{supplementary, algo 1}. The variants of DDPG and DQN
used are described in the supplementary material, as well as all the hyperparameters
used. To make comparison fair, we use the properly rescaled discount
factor $\gamma_\deltat$ and reward $r_\deltat$ from \eqref{eq:def-gamma}, as well as scaled learning rates, for DDPG and DQN.
